Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
pass over dep graph

\begin{scope}[xshift=-6cm]
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm] (goedel) { Goedel };    
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedel, node distance=2.5cm] (additions) { Additions };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=additions, node distance=2cm] (cantor) { Cantor };
\end{scope}

\begin{scope}[yshift=-0.7cm,xshift=0.25cm]
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm] (equations) { Equations };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=equations, node distance=2cm] (mathcomp) { MathComp };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,node distance=2cm,left of=equations, node distance=4.7cm] (paramcoq) { Paramcoq };
\end{scope}

\begin{scope}[yshift=-1.8cm,xshift=-4cm]
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm] (hydras) { Hydra-battles };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=hydras, node distance=2.5cm] (chains) { Addition-chains };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=chains, node distance=2.2cm] (gaia) { Gaia };
\end{scope}

\begin{scope}[yshift=-2.8cm,xshift=-6cm]
 \node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm] (goedelcc) { Goedel };
 \node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedelcc, node distance=2.2cm] (gaiahydras) { Gaia-hydras };
\end{scope}

\draw[->,dotted] (additions.south) -- (chains.north) ;
\draw[->,dotted] (goedel) -- (goedelcc) ;
\draw[->,dotted] (goedel) -- (hydras.north west) ;
\draw[->,dotted] (cantor) -- (hydras.north) ;
\draw[->,dotted] (cantor.south) -- (gaia.north west) ;
\draw[->] (hydras) -- (gaiahydras) ;
\draw[->] (gaia.south west) -- (gaiahydras.east) ;

\draw[->] (equations) -- (hydras) ;
\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (equations.south) -- (chains) ;
\draw[->] (paramcoq.south) -- (hydras) ;
\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages.}
  \label{fig:round}
\end{figure}

@@

\section{Modernizing the building infrastructure}

@@

We believe that current Coq books can broadly be divided into two categories:
\begin{itemize}
\item \emph{Executable books} that are in effect large, well-commented Coq programs from which other representations of the material (HTML, PDF) are derived using tools.
\item \emph{Traditional books} generated from documentation languages such as LaTeX that are accompanied by standalone Coq formalizations.
\end{itemize}

>>>>

\begin{scope}[xshift=-6cm]
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm] (goedel) { Goedel };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,left of=goedel, node distance=2.2cm] (pock) { Pocklington };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedel, node distance=2.5cm] (additions) { Additions };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=additions, node distance=2cm] (cantor) { Cantor };
\end{scope}

\begin{scope}[yshift=-0.7cm,xshift=0.25cm]
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm] (paramcoq) { Paramcoq };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=paramcoq, node distance=2cm] (mathcomp) { MathComp };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,node distance=2cm,left of=paramcoq, node distance=4.7cm] (equations) { Equations };
\end{scope}

\begin{scope}[yshift=-1.8cm,xshift=-4cm]
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm] (hydras) { Hydra-battles };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,left of=hydras, node distance=3.5cm] (pockcc) { Pocklington };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=hydras, node distance=2.5cm] (chains) { Addition-chains };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=chains, node distance=2.2cm] (gaia) { Gaia };
\end{scope}

\begin{scope}[yshift=-2.8cm,xshift=-6cm]
 \node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm] (goedelcc) { Goedel };
 \node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedelcc, node distance=3cm] (gaiahydras) { Gaia-hydras };
\end{scope}

\draw[->,dotted] (additions.south) -- (chains.north) ;
\draw[->,dotted] (goedel) -- (goedelcc) ;
\draw[->,dotted] (goedel) -- (hydras.north west) ;
\draw[->,dotted] (cantor) -- (hydras.north) ;
\draw[->,dotted] (cantor.south) -- (gaia.north west) ;
\draw[->] (hydras) -- (gaiahydras) ;
\draw[->] (hydras.south west) -- (goedelcc) ;
\draw[->] (gaia.south west) -- (gaiahydras.east) ;

\draw[->] (equations) -- (hydras) ;
\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\draw[->] (pock) -- (pockcc) ;
\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages.}
  \label{fig:round}
\end{figure}

@@

\section{Modernizing the build infrastructure}

@@

We believe that current Coq books can broadly be divided into two categories:
\begin{enumerate}
\item[a)] \emph{Executable textbooks} that are in effect large, well-commented Coq programs from which other representations of the material (HTML, PDF) are derived using tools.
\item[b)] \emph{Traditional textbooks} generated from documentation languages such as LaTeX that are accompanied by standalone Coq formalizations and/or code snippets.
\end{enumerate}
